HealpixNet: Efficient spherical Convolutional Neural Network with HEALPix sampling for cosmological applications

### 2018-09-03 scnn.tex
fix links in footnotes

\section*{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
	\item (TK) Check use of British vs American English. Check use of tense.
	\item (TK) Larger text on figure 2. I (MD) made it one column wide instead of two as it's more an illustration than a central figure to our exposition.
	\item (MD) Figure 4: speed for multiple lmax.
    \item (TK) check part sphere notebook and whole sphere
    \item (NP) Put Raphael in the dataset author.
    \item (Probably OK) Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
    \item (I think it is OK) (NP) Check the wording. Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
    \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
    \item Check links in footnotes.
	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly. MD: lmodern is better, but can we use it (w.r.t.\ journal policy)? If equations split out, we can try to arrange them. We should also check which font size we can / have to use.
\end{itemize}

@@

The performance of HealpixNet is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
The classification methods were trained to predict a label from a HEALPix map.
Both our Python implementation\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online. Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything.

@@

The main product of this contribution is HealpixNet: a small and easy-to-use python package for spherical analysis of cosmological data.
The code and data used in this work are publicly available\footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}.
The code was designed in a way to enable straightforward modifications of the architectures, so that HealpixNet can easily be used for a number of typical machine learning tasks, such as classification, regression, or segmentation.
Notably, for a problem of cosmological parameter estimation \citep{fluri2018deep,gupta2018nongaussianinformation}, it is easy to replace the classification loss task with a regression loss.
It should also be possible use dense layer for an output and perform segmentation tasks, such as masking, flagging, or object detection.

>>>>

\section*{TODO list}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt]
	\item (TK) Can we use HEALPix in the name? Check with the main author of HEALPix. MD: what about DeepCosmo or CosmoNet? NP: cosmological data is not necessarily spherical.
	\item (TK) Check use of British vs American English. Check use of tense.
	\item (TK) Larger text on figure 2. I (MD) made it one column wide instead of two as it's more an illustration than a central figure to our exposition.
	\item (MD) Figure 4: speed for multiple lmax.
    \item (TK) check part sphere notebook and whole sphere
    \item (NP) Put Raphael in the dataset author.
    \item (Probably OK) Beware to not confuse reader with synonyms, e.g. pixelization and sampling.
    \item (I think it is OK) (NP) Check the wording. Be sure that the convolution on SO(3) is clear: we want to say (a) is the one associated with the SO(3) rotation group (b) can be performed  in the spectral domain by a multiplication (c) is equivariant to rotation (d) is described well in Section 2 of \citep{kondor2018clebsch}.
    \item (Everyone should check this) Notation: write element $i$ of vector $y$ as $y_i$, $y(i)$, or $y[i]$? Be consistent. Same for matrices. Keep indices.
	\item (fail - I checked few fonts here: \url{de.sharelatex.com/learn/Font_typefaces}, but none looked better) (TK) Font: do we have to use times (set in the documentclass)? I (MD) find the rendering of math a bit ugly. MD: lmodern is better, but can we use it (w.r.t.\ journal policy)? If equations split out, we can try to arrange them. We should also check which font size we can / have to use.
\end{itemize}

@@

The performance of HealpixNet is demonstrated on a discrimination problem: the classification of convergence maps into two cosmological model classes.
The experiment presented here is similar to the one by \citep{schmelze2017cosmologicalmodel}.
These maps are similar to those created with gravitational lensing techniques \citep{chang2017curvedsky}.
The two sets of maps were created using the standard cosmological model with two sets of cosmological parameters.
The classification methods were trained to predict a label from a HEALPix map.
Both our Python implementation{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}} and the data\footnote{\url{https://doi.org/10.5281/zenodo.1303272}} to reproduce those experiments are openly available online. Furthermore, Jupyter notebooks demoing the method and problem can be run from your browser without installing anything.

@@

The main product of this contribution is HealpixNet: a small and easy-to-use python package for spherical analysis of cosmological data.
The code and data used in this work are publicly available{\interfootnotelinepenalty=10000 \footnote{\url{https://github.com/SwissDataScienceCenter/HealpixNet}}}.
The code was designed in a way to enable straightforward modifications of the architectures, so that HealpixNet can easily be used for a number of typical machine learning tasks, such as classification, regression, or segmentation.
Notably, for a problem of cosmological parameter estimation \citep{fluri2018deep,gupta2018nongaussianinformation}, it is easy to replace the classification loss task with a regression loss.
It should also be possible use dense layer for an output and perform segmentation tasks, such as masking, flagging, or object detection.
